Teams analyses

### 2022-04-19 scripts/r/teams-analyses.Rmd
♻️ - update analysis questionnaire

```{r team-analyses}
teams_analyses <- read_csv("data/questionnaires/msa_data_analysis_questionnaire_April 17, 2022_06.35.csv") %>%
  # Get rid of unused columns
  select(-(EndDate:UserLanguage))

@@

```{r review}
the_sheet <- "https://docs.google.com/spreadsheets/d/1vFPjZkB4naCNj10v0BuEWQDvo34okmcN1Mv7VkZL9po/edit#gid=0"

>>>>

```{r team-analyses}
teams_analyses <- read_csv("data/questionnaires/msa_data_analysis_questionnaire_April 19, 2022_08.06.csv") %>%
  # Get rid of unused columns
  select(-(EndDate:UserLanguage))

@@

```{r review, eval=FALSE}
the_sheet <- "https://docs.google.com/spreadsheets/d/1vFPjZkB4naCNj10v0BuEWQDvo34okmcN1Mv7VkZL9po/edit#gid=0"
